---
title: "p8105_hw1_yo2336"
author: "Yoo Rim Oh"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```
 
# Problem 1


## Create data frame

data frame created using tibble named hw_df 
with numerical vector from Normal distribution (vec_rnorm),
logical vector indicating if each elements of numerical vector are > 0 (vec_logical),
character vector assigned from A to J (vec_char),
and factor vector with 3 levels: small, medium, and large (vec_factor)

set.seed used for reproducibility, generating only one random sample for vec_rnorm each time code ran

```{r}
set.seed(10)

hw_df = tibble(
  vec_rnorm = rnorm(10),
  vec_logical = vec_rnorm > 0,
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_factor = factor(c("small", "small","large","medium","large",
                        "small","medium","small","large","large"))
)
```

## Means of each variables

pulled each vector at a time from data frame (hw_df) to compute mean.

only the numerical vector from Normal distribution (vec_rnorm) and 
logical vector (vec_logical) able to generate mean.

```{r}
mean(pull(hw_df, vec_rnorm))

mean(pull(hw_df, vec_logical))

mean(pull(hw_df, vec_char))

mean(pull(hw_df, vec_factor))
```



## as.numeric function applied to variables


vec_logical and vec_factor converted into numerical form but not vec_char.

```{r, eval = FALSE}
as.numeric(pull(hw_df, vec_logical))

as.numeric(pull(hw_df, vec_char))

as.numeric(pull(hw_df, vec_factor))
```

Each components of vec_logical converted into numerical form, 1 = True and 0 = False. 
True if the numerical values of vec_rnorm are > 0.

Each ordinal levels of vec_factor also converted into numerical form, 
1 = large, 2 = medium, and 3 = small.




# Problem 2


## Load dataset Penguins


```{r}
data("penguins", package = "palmerpenguins")
```

## Penguin data description

print() to see Penguins data.

summary() to see brief description of data.

```{r}
print(penguins)
summary(penguins)

nrow(penguins)
ncol(penguins)

mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```

Penguins data has 8 columns indicating variables: species, island, bill_length_mm, bill_depth_mm, 
flipper_length_mm, body_mass_g, sex, and year.
It has 344 rows, representing 344 sets of data collected.

pulled flipper_length_mm only from penguins data to compute mean.
na.rm = TRUE used to exclude 2 missing data points for flipper_length_mm when computing mean.


## Scatter plot of Penguins and Export plot


```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()


ggsave("penguin_scatter_plot.pdf", height = 4, width = 4)
```

ggplot to create scatter plot (using geom_point()).

ggsave to export plot into a pdf form.
