---
title: "p8105_hw1_yo2336"
author: "Yoo Rim Oh"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```
 
# Problem 1


## Create data frame

data frame named hw_df 
with numerical vector from Normal distribution,
logical vector indicating if each elements of numerical vector > 0,
character vector named from A to J,
and factor vector with 3 levels: small, medium, and large

set.seed used for reproducibility 

```{r}
set.seed(10)

hw_df = tibble(
  vec_rnorm = rnorm(10),
  vec_logical = vec_rnorm > 0,
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_factor = factor(c("small", "small","large","medium","large","small","medium","small","large","large"))
)
```

## Means of each variables


only the numerical vector from Normal distribution (vec_rnorm) and logical vector (vec_logical) able to generate mean

```{r}
mean(pull(hw_df, vec_rnorm))

mean(pull(hw_df, vec_logical))

mean(pull(hw_df, vec_char))

mean(pull(hw_df, vec_factor))
```



## as.numeric function applied to variables


vec_logical and vec_factor converted into numerical form but not vec_char

```{r, eval = FALSE}
as.numeric(pull(hw_df, vec_logical))

as.numeric(pull(hw_df, vec_char))

as.numeric(pull(hw_df, vec_factor))
```




# Problem 2


## Load dataset Penguins


```{r}
data("penguins", package = "palmerpenguins")
```

## Penguin data description


```{r}
print(penguins)
summary(penguins)

nrow(penguins)
ncol(penguins)

mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```



## Scatter plot of Penguins and Export plot


```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()


ggsave("penguin_scatter_plot.pdf", height = 4, width = 4)
```

